Grappa: Scalable Computing on Commodity Hardware \\for Irregular Applications

### 2012-07-23 doc/asplos13/evaluation.tex
prestons edits

We ran UTS-mem on Grappa and the XMT with a binomial and two geometric
100M-vertex trees (T3L,T1L,T2L), a geometric 1.6B-vertex tree (T1XL),
and a geometric 4.2B-vertex tree (T1XXL). Both systems do relatively
poorly on the binomial tree because it is very deep and a traversal
produces too little parallelism. Figure~\ref{fig:grappa-xmt-uts} shows
the performance in terms of number of vertices visited per second versus
number of compute nodes. The Grappa results shown are for 6 cores per
node and the best parameter values from a search over runtime and
application parameters.

@@

Figure~\ref{fig:bfs-performance} shows Grappa's performance on BFS
compared to that of the XMT\footnote{The performance dip at 112 nodes is not an anomaly.  It is highly repeatable.  Despite extensive investigation on our part, we can find no reasonable explanation for it.}. There are
two things to observe. First, At 128 XMT processors/cluster nodes,
the XMT is  4.17 times faster than Grappa. This is due to the
XMT's faster network: the XMT is able to issue 100 million network
requests per second per node; at the 128 nodes datapoint, Grappa is
aggregating 25 million network requests per second, or 4 times slower.
\checkme{Second, Grappa is scaling...}

>>>>

We ran UTS-mem on Grappa and the XMT with a binomial and two geometric
100M-vertex trees (T3L,T1L,T2L), a geometric 1.6B-vertex tree (T1XL),
and a geometric 4.2B-vertex tree (T1XXL). Both systems do relatively
poorly on the binomial tree because it is very deep and a traversal
produces too little parallelism. Figure~\ref{fig:uts_compare} shows
the performance in terms of number of vertices visited per second versus
number of compute nodes. The Grappa results shown are for 6 cores per
node and the best parameter values from a search over runtime and
application parameters.

@@

Figure~\ref{fig:bfs-performance} shows Grappa's performance on BFS
compared to that of the XMT.\footnote{The performance dip at 112 nodes is not an anomaly; it is highly repeatable.  Despite extensive investigation on our part, we can find no reasonable explanation for it.} There are
two things to observe. First, At 128 XMT processors/cluster nodes,
the XMT is  4.17 times faster than Grappa. This is due to the
XMT's faster network: the XMT is able to issue 100 million network
requests per second per node; at the 128 nodes datapoint, Grappa is
aggregating 25 million network requests per second, or 4 times slower.
\checkme{Second, Grappa is scaling...}
